---
title: "Step01_Organize_Propensity_Data.Rmd"
output: html_notebook
---
This R Notebook documents the steps taken to organize the data used for CU propensity matching projects for the ABCD Dataset. 

First, install necessary packages. 

```{r}
library(MatchIt)
library(boxr)
library(tidyr)
library(dplyr)
library(cobalt)
library(ggplot2)
library(finalfit)
library(haven)
library(gghalves)
library(usmap)
library(bcf)
```

Specify that select function should be pulled from dplyr
```{r}
select <- dplyr::select
recode<- dplyr::recode
mutate<- dplyr::mutate
```

Next, log into PennBox, and set working directory the ABCD directory. We are using WAVE 5 Data for this project. 
```{r}
box_auth()

box_setwd('167848222541')
```

---
Step 1: Organize Data
---

Read in CBCL + SDQ to make a CU baseline traits score:
```{r}
cbcl<-box_read('1277090142488')
cbcl_cu<- as_tibble(cbcl)%>%
  filter(eventname == "baseline_year_1_arm_1")%>%
  select(starts_with(c("src_subject_id", "cbcl_q26_p")))

sdq<-box_read('1277071581025')
sdq_cu<-as_tibble(sdq) %>%
  filter(eventname == "baseline_year_1_arm_1")%>%
  select(starts_with(c("src_subject_id","prosocial_q1_p","prosocial_q2_p","prosocial_q3_p")))%>%
  mutate(prosocial_q1_p=recode(prosocial_q1_p, "2" = 0, "1"=1, "0" = 2))%>% #reverse code
  mutate(prosocial_q2_p=recode(prosocial_q2_p, "2" = 0, "1"=1, "0" = 2))%>% #reverse code
  mutate(prosocial_q3_p=recode(prosocial_q3_p, "2" = 0, "1"=1, "0" = 2)) #reverse code 
  
cu_score<- merge(cbcl_cu, sdq_cu, by="src_subject_id", all=T)%>%
  mutate_at(vars(-c("src_subject_id")),as.numeric)%>%
  mutate(cu_t1= cbcl_q26_p+prosocial_q1_p+prosocial_q2_p+prosocial_q3_p)%>%
  mutate(cu_bin = case_when(cu_t1 >= 4 ~ 1, 
                            cu_t1  == 0 ~ 0))%>%
  select(src_subject_id, cu_t1, cu_bin)


table(cu_score$cu_bin)
```

Read in data used for creation of propensity score: 
```{r}
ext_p<- box_read('1277091056577')%>%
  filter(eventname == 'baseline_year_1_arm_1')%>%
  select(src_subject_id, asr_scr_external_t)%>%
  mutate(across(everything(), ~ifelse(.=="777", NA, as.character(.))))%>% #recode "unknown" cells as "NA" 
  mutate(across(everything(), ~ifelse(.=="999", NA, as.character(.))))#recode "refused" cells as "NA"

warmth_y<- box_read('1277078742059')%>%
  filter(eventname == 'baseline_year_1_arm_1')%>%
  select(src_subject_id, crpbi_y_ss_parent)%>%
  mutate(across(everything(), ~ifelse(.=="777", NA, as.character(.))))%>% #recode "unknown" cells as "NA" 
  mutate(across(everything(), ~ifelse(.=="999", NA, as.character(.))))#recode "refused" cells as "NA"

chaos_y<- box_read('1277078756459')%>%
  filter(eventname == 'baseline_year_1_arm_1')%>%
  select(src_subject_id, fes_y_ss_fc)%>%
  mutate(across(everything(), ~ifelse(.=="777", NA, as.character(.))))%>% #recode "unknown" cells as "NA" 
  mutate(across(everything(), ~ifelse(.=="999", NA, as.character(.))))#recode "refused" cells as "NA"
  
demos<-box_read('1277081419111')%>%
  filter(eventname == 'baseline_year_1_arm_1')%>%
  select(src_subject_id, demo_brthdat_v2, eventname, demo_sex_v2, demo_prnt_ed_v2, demo_comb_income_v2,
         demo_ethn_v2)%>%
  mutate(across(everything(), ~ifelse(.=="777", NA, as.character(.))))%>% #recode "unknown" cells as "NA" 
  mutate(across(everything(), ~ifelse(.=="999", NA, as.character(.))))#recode "refused" cells as "NA"

ids<-box_read('1277070740402', fread=T)
ids$site_id_l<-gsub('site','',ids$site_id_l)
ids<-ids%>%
  filter(eventname == 'baseline_year_1_arm_1')%>%
  select(src_subject_id, site_id_l, rel_family_id)

race<- box_read('1052335592112', fread=T)
race<- race %>%
  mutate(binary_race= case_when(race3 == 1 ~ 0, 
                                FALSE ~ 1))%>%
  mutate(src_subject_id = subjectkey)%>%
  select(src_subject_id, binary_race)
```
Read in cortical and subcortical cGM 
```{r}
cortical<- box_read('1277074343528')
subcort<- box_read('1277081154026')

imaging<- merge(subcort, cortical)

imaging<- imaging %>%
  filter(eventname %in% c('baseline_year_1_arm_1'))%>%
  select(starts_with(c('src_subject_id', 'smri_vol_scs_amygdala', 'smri_vol_cdk_rracate', 'smri_vol_cdk_cdacate')))%>%
  mutate(bilateral_amygdala = smri_vol_scs_amygdalalh +smri_vol_scs_amygdalarh)%>%
  mutate(bilateral_acc = smri_vol_cdk_rracatelh +smri_vol_cdk_rracaterh + smri_vol_cdk_cdacatelh +smri_vol_cdk_cdacaterh)%>%
  select(starts_with(c('src_subject_id', 'bilateral')))
```

Merge together into one dataset: 
```{r}
propensity_data<- merge(ids, cu_score)
propensity_data<- merge(propensity_data, demos)
propensity_data<- merge(propensity_data, ext_p)
propensity_data<- merge(propensity_data, warmth_y)
propensity_data<- merge(propensity_data, chaos_y)
propensity_data<- merge(propensity_data, race)
propensity_data<- merge(propensity_data, imaging)
```

Standardize v's: 
```{r}
propensity_data<- propensity_data%>%
  na.omit(cu_bin)%>%
  mutate(
    cu_bin = as.integer(cu_bin), 
    site_id_l = factor(site_id_l))%>%
  mutate(across(all_of(c("demo_comb_income_v2", "crpbi_y_ss_parent", "fes_y_ss_fc", "asr_scr_external_t", 
                         "bilateral_amygdala", "bilateral_acc")),
                as.numeric)) %>%
  mutate(across(c(demo_comb_income_v2, crpbi_y_ss_parent, fes_y_ss_fc, asr_scr_external_t, bilateral_amygdala, bilateral_acc), 
                ~ as.numeric(scale(.x)), 
                .names = "{.col}_z"))
```

Create the propensity weights for CU traits using parenting, genetic risk, and household income
```{r}
p_cu <- glmer(cu_bin ~ demo_comb_income_v2_z +  crpbi_y_ss_parent_z + fes_y_ss_fc_z+ 
                asr_scr_external_t_z + demo_sex_v2 +  bilateral_amygdala_z +
                bilateral_acc_z + (1 | site_id_l),
               na.action=na.exclude, 
               family = binomial, data = propensity_data)

summary(p_cu)

propensity_data$p_cu <- predict(p_cu, type = "response")
```

Show distributions of propensity scores: 
```{r}
ggplot(propensity_data, aes(x = p_cu, fill = as.factor(cu_bin))) +
  geom_density(alpha = 0.5) +
  labs(x = "Predicted probability of CU group",
       y = "Density",
       fill = "Observed group") +
  scale_fill_manual(labels = c('Low CU', 'High CU'), values = c('#C1CFCA', '#06948E'), name = "CU Group") +
  theme_classic() + theme(legend.box.background = element_rect(color = "black", size = .75), 
                                                       text = element_text(size=14))+ theme(legend.position = c(0.8, 0.8))
```

---
Describe sample
---

Demo table 
```{r}
demo_table_data <- propensity_data %>%
  select(demo_sex_v2, demo_comb_income_v2, demo_brthdat_v2, cu_bin, demo_ethn_v2)%>%
  mutate(sex = dplyr::recode(demo_sex_v2, `1`='Female', `2`='Male')) %>%
  mutate(
    income = case_when(
      demo_comb_income_v2 == 1 ~ 'Less than $5,000', 
      demo_comb_income_v2 == 2 ~ '$5,000 - $11,999', 
      demo_comb_income_v2 == 3 ~ '$12,000 through $15,999', 
      demo_comb_income_v2 == 4 ~ '$16,000 through $24,999', 
      demo_comb_income_v2 == 5 ~ '$25,000 through $34,999', 
      demo_comb_income_v2 == 6 ~ '$35,000 through $49,999',
      demo_comb_income_v2 == 7 ~ '$50,000 through $74,999',
      demo_comb_income_v2 == 8 ~ '$75,000 through $99,999',
      demo_comb_income_v2 == 9 ~ '$100,000 through $199,999',
      demo_comb_income_v2 == 10 ~ '$200,000 and greater',
      demo_comb_income_v2 == 999 ~ 'NA',
      demo_comb_income_v2 == 777 ~ 'NA',
      TRUE ~ 'NA'))%>%
  mutate(race_char = case_when(demo_ethn_v2 == 2 ~ "Non Hispanic", 
                               demo_ethn_v2 == 1 ~ "Hispanic", 
                               TRUE ~ "Not reported"))%>%
  mutate(race_char = as.character(race_char))%>%
  mutate(demo_brthdat_v2 = as.numeric(demo_brthdat_v2))

table(demo_table_data$race_char)

demo_table_data %>%
  set_column_labels(sex = "Sex", 
                    demo_brthdat_v2 = "Age (Months)",
                    income = "Household Income", 
                    race_char = "Reported Ethnicity") %>%
Gmisc::getDescriptionStatsBy(sex, demo_brthdat_v2, income,race_char,
                      add_total_col = TRUE, statistics=TRUE,show_all_values=TRUE,
                      by = cu_bin)

#table(clusters$assignment_2)

```

Random plots for presentation
```{r}
#map
highlighted_states <- c("OR","CA","UT","CO","OK","MN","WI","MI",
                        "FL","SC","VA","DC","PA","NY","RI","VT","MD")

all_states <- unique(usmap::us_map("states")$abbr)

state_data <- data.frame(
  state  = all_states,
  color  = "#D3D3D3"          # light grey
)
state_data$color[state_data$state %in% highlighted_states] <- "#06948E"

plot_usmap(data= state_data, values="color", color="white") + scale_fill_identity()  +
  theme(legend.position='none')

#pie charts
cu_counts <- cu_score %>%
  mutate(ses_bin = case_when(
    cu_bin == 0 ~ 'No CU Traits',
    cu_bin == 1 ~ 'High CU Traits',
    TRUE ~ "Not Included"
  )) 
cu_counts <- as.data.frame(table(cu_counts$ses_bin))
colnames(cu_counts) <- c("CU Traits", "count")
cu_counts$percent <- cu_counts$count / sum(cu_counts$count) * 100

sex_counts <- propensity_data %>%
  mutate(sex_bin = case_when(
    demo_sex_v2 == 1 ~ 'Male',
    demo_sex_v2 == 2 ~ 'Female',
    TRUE ~ "N/A"
  )) 
sex_counts <- as.data.frame(table(sex_counts$sex_bin))
colnames(sex_counts) <- c("Sex", "count")
sex_counts$percent <- sex_counts$count / sum(sex_counts$count) * 100

# Create the pie chart
ggplot(cu_counts, aes(x = "", y = count, fill = `CU Traits`)) +
  geom_bar(width = 1, stat = "identity", color = 'white', alpha=.5) +
  coord_polar("y", start = 0) +
  scale_fill_manual(values = c("#06948E","#E69965",'lightgrey'))+
  theme_void() +
  theme(plot.title = element_text(hjust = 0.5))

ggplot(sex_counts, aes(x = "", y = count, fill = `Sex`)) +
  geom_bar(width = 1, stat = "identity", color = 'white', alpha=.5) +
  coord_polar("y", start = 0) +
  scale_fill_manual(values = c("#06948E","#E69965"))+
  theme_void() +
  theme(plot.title = element_text(hjust = 0.5))


race<- box_read('1052335592112')
race<- merge(race, propensity_data, by.x ='subjectkey', by.y='src_subject_id')
race_counts <- as.data.frame(table(race$race3))
colnames(race_counts) <- c("Race", "count")
race_counts$percent <- race_counts$count / sum(race_counts$count) * 100

ggplot(race_counts, aes(x = "", y = count, fill = `Race`)) +
  geom_bar(width = 1, stat = "identity", color = 'white', alpha=.8) +
  coord_polar("y", start = 0) +
  scale_fill_manual(values = c("#06948E", "#4DA8A2", "#8ABCB6", "#C1CFCA", "#D3D3D3"), 
                    labels = c("White", "Black/African American", "Asian", "More than one race","Other"))+
  theme_void() +
  theme(plot.title = element_text(hjust = 0.5))

set.seed(42)

x <- runif(100, 0, 50)          
y <- 2 * x + rnorm(100, mean = 0, sd = 10)
scatter_df <- data.frame(x = x, y = y)

ggplot(scatter_df, aes(x=x, y=y)) +geom_point(color='#06948E') + geom_smooth(method='lm', color='#06948E', fill='#06948E') +
  theme_classic()


hist_df<- data.frame(x=rnorm(100, mean = 50, sd = 20), 
                     y=rnorm(100, mean = 110, sd = 10), 
                     z=rnorm(100, mean = 100, sd = 8))%>%
  pivot_longer(cols = c(x,y,z))

ggplot(hist_df, aes(x=value, group=name, fill=name)) + geom_density(alpha=0.5) +scale_fill_manual(values = c("#06948E", 
                                                                                                              "#8ABCB6", 
                                                                                                              "#C1CFCA"))+
  theme_void()
```

Now read in our moderator data: 
```{r}
#read in area deprivation index 
adi<-box_read('1277087025313', fread=TRUE)
adi<-adi%>%
  filter(eventname=="baseline_year_1_arm_1")%>%
  mutate(adi_bin = case_when(reshist_addr1_adi_wsum <= 87.862045 ~ 0, #low deprivation
                             reshist_addr1_adi_wsum >= 108.394920 ~ 1))%>% #high deprivation
  mutate(adi_bin_SENS = case_when(reshist_addr1_adi_wsum < 98.777885 ~ 0, #low deprivation
                             reshist_addr1_adi_wsum >= 98.777885 ~ 1))%>% #high deprivation
  select(src_subject_id, reshist_addr1_adi_wsum, adi_bin, adi_bin_SENS)

#read in greenspace
green<-box_read('1277088493816', fread=TRUE)
green<-green%>%
  filter(eventname=="baseline_year_1_arm_1")%>%
  mutate(green_bin = case_when(reshist_addr1_coi_he_green <= 14 ~ 0, #low green
                             reshist_addr1_coi_he_green >= 48.025 ~ 1))%>% #high green
  mutate(green_bin_SENS = case_when(reshist_addr1_coi_he_green < 34.100 ~ 0, #low green
                             reshist_addr1_coi_he_green >= 34.100 ~ 1))%>% #high green
  select(src_subject_id, reshist_addr1_coi_he_green, green_bin, green_bin_SENS)

#read in geocoded crime
crime<-box_read('1277095261533', fread=TRUE)
crime<- crime%>%
  filter(eventname=="baseline_year_1_arm_1")%>%
  mutate(crime_log = log(reshist_addr1_grndtot +1))%>%
  mutate(crime_bins = cut(reshist_addr1_grndtot, breaks = 6))%>%
  mutate(crime_bin = case_when(reshist_addr1_grndtot <= 7832.00 ~ 0, 
                               reshist_addr1_grndtot >= 53399.67 ~ 1))%>%
  mutate(crime_bin_SENS = case_when(reshist_addr1_grndtot < 22761.33 ~ 0, 
                               reshist_addr1_grndtot >= 22761.33 ~ 1))%>%
  select(src_subject_id, reshist_addr1_grndtot, crime_bin, crime_bin_SENS)
```

And outcome data: 
```{r}
#cbcl data is already loaded from the CU traits score
cbcl_dsm<- cbcl%>%
  select(starts_with(c("src_subject_id","interview_age", "eventname",
                       "cbcl_scr_syn_external_t", "cbcl_scr_dsm5_conduct_t", 
                       "cbcl_scr_dsm5_opposit_t", "cbcl_scr_dsm5_adhd_t")))%>%
  pivot_wider(names_from = eventname, values_from = c(cbcl_scr_syn_external_t, cbcl_scr_dsm5_conduct_t, 
                                                      cbcl_scr_dsm5_opposit_t, cbcl_scr_dsm5_adhd_t))%>%
  rename_with(~ tolower(gsub("baseline_year_1_arm_1", "t1", .x, fixed = TRUE))) %>% 
  rename_with(~ tolower(gsub("2_year_follow_up_y_arm_1", "t3", .x, fixed = TRUE))) %>%
  rename_with(~ tolower(gsub("1_year_follow_up_y_arm_1", "t2", .x, fixed = TRUE))) %>% 
  rename_with(~ tolower(gsub("3_year_follow_up_y_arm_1", "t4", .x, fixed = TRUE))) %>%
  rename_with(~ tolower(gsub("4_year_follow_up_y_arm_1", "t5", .x, fixed = TRUE)))
```

And merge:
```{r}
all_data<- merge(propensity_data, green)
all_data<- merge(all_data, adi)
all_data<- merge(all_data, crime)
all_data<- merge(all_data, cbcl_dsm)
```

Impute missing data: 
```{r, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
all_data<- all_data %>%
  mutate(across(all_of(c("demo_sex_v2", "demo_brthdat_v2", "demo_ethn_v2", "demo_prnt_ed_v2")), as.numeric)) 

imputed_data<- mice(all_data, m=5, method='pmm', seed=1234)
completed_data <- complete(imputed_data)
```

Save data: 
```{r}
#write.csv(completed_data, file='bcf_completed_data.csv', row.names=F)
```

```{r}
table_1_data<- all_data %>%
  select(demo_sex_v2, demo_comb_income_v2, demo_brthdat_v2, cu_bin, demo_ethn_v2, 
         crpbi_y_ss_parent_z, fes_y_ss_fc_z,
        asr_scr_external_t_z,  bilateral_amygdala_z, bilateral_acc_z, cbcl_scr_dsm5_conduct_t_t1, cbcl_scr_dsm5_adhd_t_t1, cbcl_scr_dsm5_opposit_t_t1, 
        cbcl_scr_dsm5_conduct_t_t3, cbcl_scr_dsm5_adhd_t_t3, cbcl_scr_dsm5_opposit_t_t3, reshist_addr1_grndtot, reshist_addr1_coi_he_green, reshist_addr1_adi_wsum)%>%
  mutate(sex = dplyr::recode(demo_sex_v2, `1`='Female', `2`='Male')) %>%
  mutate(
    income = case_when(
      demo_comb_income_v2 == 1 ~ 'Less than $5,000', 
      demo_comb_income_v2 == 2 ~ '$5,000 - $11,999', 
      demo_comb_income_v2 == 3 ~ '$12,000 through $15,999', 
      demo_comb_income_v2 == 4 ~ '$16,000 through $24,999', 
      demo_comb_income_v2 == 5 ~ '$25,000 through $34,999', 
      demo_comb_income_v2 == 6 ~ '$35,000 through $49,999',
      demo_comb_income_v2 == 7 ~ '$50,000 through $74,999',
      demo_comb_income_v2 == 8 ~ '$75,000 through $99,999',
      demo_comb_income_v2 == 9 ~ '$100,000 through $199,999',
      demo_comb_income_v2 == 10 ~ '$200,000 and greater',
      demo_comb_income_v2 == 999 ~ 'NA',
      demo_comb_income_v2 == 777 ~ 'NA',
      TRUE ~ 'NA'))%>%
  mutate(race_char = case_when(demo_ethn_v2 == 2 ~ "Non Hispanic", 
                               demo_ethn_v2 == 1 ~ "Hispanic", 
                               TRUE ~ "Not reported"))%>%
  mutate(race_char = as.character(race_char))%>%
  mutate(demo_brthdat_v2 = as.numeric(demo_brthdat_v2))

table(table_1_data$race_char)

table_1_data %>%
  set_column_labels(sex = "Sex", 
                    demo_brthdat_v2 = "Age (Months)",
                    income = "Household Income", 
                    race_char = "Reported Ethnicity", 
                    crpbi_y_ss_parent_z = 'Parental Warmth', 
                    fes_y_ss_fc_z = 'Family Conflict',
                    asr_scr_external_t_z = 'Parent Externalizing', 
                    bilateral_amygdala_z = 'Bilateral Amygdala Volume', 
                    bilateral_acc_z = 'Bilateral ACC Volume',
                    reshist_addr1_adi_wsum = 'Area Deprivation Index', 
                    reshist_addr1_coi_he_green = 'Access to Green Space', 
                    reshist_addr1_grndtot = 'Exposure to Crime',
                    cbcl_scr_dsm5_conduct_t_t1 = 'CD Symptoms (T1)', 
                    cbcl_scr_dsm5_adhd_t_t1 = 'ADHD Symptoms (T1)', 
                    cbcl_scr_dsm5_opposit_t_t1 = 'ODD Symptoms (T1)', 
                    cbcl_scr_dsm5_conduct_t_t3 = 'CD Symptoms (T3)', 
                    cbcl_scr_dsm5_adhd_t_t3 = 'ADHD Symptoms (T3)', 
                    cbcl_scr_dsm5_opposit_t_t3 = 'ODD Symptoms (T3)'
                     ) %>%
Gmisc::getDescriptionStatsBy(crpbi_y_ss_parent_z, fes_y_ss_fc_z,
        asr_scr_external_t_z,  bilateral_amygdala_z, bilateral_acc_z, reshist_addr1_adi_wsum, reshist_addr1_coi_he_green, reshist_addr1_grndtot, 
        cbcl_scr_dsm5_conduct_t_t1, cbcl_scr_dsm5_adhd_t_t1, cbcl_scr_dsm5_opposit_t_t1, 
        cbcl_scr_dsm5_conduct_t_t3, cbcl_scr_dsm5_adhd_t_t3, cbcl_scr_dsm5_opposit_t_t3,
                      add_total_col = TRUE, statistics=TRUE,show_all_values=TRUE,
                      by = cu_bin)

```


Save function to run anova: 
```{r}
# Define function to run anova tests
run_anova <- function(y_var, predictor, data) {
  # Dynamically construct the formula
  formula <- as.formula(paste(y_var, "~", predictor))
  # Run linear model (ANCOVA)
  lm_model <- lm(formula, data = data)
  
  # Summarize the linear model
  anova_summary <- summary(aov(lm_model))
  
  # Extract relevant ANOVA table information
  result_table <- as.data.frame(anova_summary[[1]])%>%
    rownames_to_column("term")%>%
    mutate(statistic = `F value`)%>%
    mutate(p.value = `Pr(>F)`)%>%
    select(term, statistic, p.value) %>%
    mutate(variable = y_var)
  result_table <- result_table[-2, ]
  
  descriptives <- data %>%
    group_by(.data[[predictor]]) %>%
    summarise(
      M  = mean(.data[[y_var]], na.rm = TRUE),
      SD = sd(.data[[y_var]], na.rm = TRUE),
      .groups = "drop"
    ) %>%
    mutate(group = as.character(.data[[predictor]])) %>%
    select(-all_of(predictor)) %>%
    pivot_wider(
      names_from  = group,
      values_from = c(M, SD),
      names_glue  = "{.value}_{group}"
    )
  
  # Bind ANOVA + descriptives
  final_table <- bind_cols(result_table, descriptives)%>%
    select(starts_with(c("term", "statistic", "p.value", "variable", "M_0", "M_1", "SD_0", "SD_1")))
  
  return(final_table)
}
```

Compare v's based on CU 
```{r}
vars<- c('demo_comb_income_v2_z',  'crpbi_y_ss_parent_z', 'fes_y_ss_fc_z',
        'asr_scr_external_t_z',  'bilateral_amygdala_z', 'bilateral_acc_z')

anova_cu <- map_dfr(vars, ~ run_anova(.x, data = completed_data, predictor = 'cu_bin'))
anova_adi <- map_dfr(vars, ~ run_anova(.x, data = completed_data, predictor = 'adi_bin'))
anova_crime <- map_dfr(vars, ~ run_anova(.x, data = completed_data, predictor = 'crime_bin'))
anova_green <- map_dfr(vars, ~ run_anova(.x, data = completed_data, predictor = 'green_bin'))
```
```{r}
all_anova<- rbind(anova_cu, anova_adi, anova_crime, anova_green)

results_table<- all_anova%>%
  mutate(variable = dplyr::recode(variable, 'demo_comb_income_v2_z' = 'Household Income', 
                       'crpbi_y_ss_parent_z' = 'Parental Warmth', 
                       'fes_y_ss_fc_z' = 'Family Conflict',
                       'asr_scr_external_t_z' = 'Parent Externalizing', 
                       'bilateral_amygdala_z' = 'Bilateral Amygdala Volume', 
                       'bilateral_acc_z' = 'Bilateral ACC Volume'))%>%
  mutate(statistic = round(statistic, 2))%>%
  mutate(p.value = round(p.value, 3))%>%
  mutate(M_SD_0 = paste0(round(M_0, 2), " ", "(", round(SD_0,2), ")"))%>%
  mutate(M_SD_1 = paste0(round(M_1,2), " ", "(", round(SD_1,2), ")"))%>%
  select(-c(M_0, M_1, SD_0, SD_1))%>%
  pivot_wider(values_from = c(statistic, p.value, M_SD_0, M_SD_1), names_from = term)%>%
  gt()%>%
  tab_header(
    title = md("**Table X. Comparisons on**")
  ) %>%
  tab_spanner(label = "CU Traits", columns = starts_with(c("statistic_cu_bin", "p.value_cu_bin", "M_SD_0_cu_bin", "M_SD_1_cu_bin")))%>%
  tab_spanner(label = "ADI", columns = starts_with(c("statistic_adi_bin", "p.value_adi_bin", "M_SD_0_adi_bin", "M_SD_1_adi_bin")))%>%
  tab_spanner(label = "Crime", columns = starts_with(c("statistic_crime_bin","p.value_crime_bin", "M_SD_0_crime_bin", "M_SD_1_crime_bin")))%>%
  tab_spanner(label = "Green Space", columns = starts_with(c("statistic_green_bin", "p.value_green_bin", "M_SD_0_green_bin", "M_SD_1_green_bin")))
    
results_table
```

```{r}
propensity_data_long <- completed_data %>%
  pivot_longer(cols = c("demo_comb_income_v2_z", "crpbi_y_ss_parent_z", "fes_y_ss_fc_z", "asr_scr_external_t_z", "bilateral_amygdala_z", 
                        "bilateral_acc_z"))%>%
  mutate(name = recode(name, 'demo_comb_income_v2_z' = 'Household Income', 
                       'crpbi_y_ss_parent_z' = 'Parental Warmth', 
                       'fes_y_ss_fc_z' = 'Family Conflict',
                       'asr_scr_external_t_z' = 'Parent Externalizing', 
                       'bilateral_amygdala_z' = 'Bilateral Amygdala Volume', 
                       'bilateral_acc_z' = 'Bilateral ACC Volume'))

cu_anova<- ggplot(propensity_data_long, aes(y = value, x = name, fill = as.factor(cu_bin))) +
  geom_half_violin(
    data = subset(propensity_data_long, cu_bin == 1),
    aes(group = interaction(name, as.factor(cu_bin))),  # keep grouping explicit
    side = "l", position = position_dodge(width = 0.64),
    width = 0.8, alpha = 0.8, scale = "count", trim = FALSE
  ) +
  geom_half_violin(
    data = subset(propensity_data_long, cu_bin == 0),
    aes(group = interaction(name, as.factor(cu_bin))),
    side = "r", position = position_dodge(width = 0.4),
    width = 1, alpha = 0.8, scale = "count", trim = FALSE
  ) + geom_half_boxplot(
    data = subset(propensity_data_long, cu_bin == 1),
    aes(group = interaction(name, as.factor(cu_bin))),  # keep grouping explicit
    side = "l", position = position_dodge(width = 0.6),
    width = 0.1, alpha = 0.8, scale = "count", trim = FALSE
  ) +
  geom_half_boxplot(
    data = subset(propensity_data_long, cu_bin == 0),
    aes(group = interaction(name, as.factor(cu_bin))),
    side = "r", position = position_dodge(width = 0.6),
    width = 0.1, alpha = 0.8, scale = "count", trim = FALSE
  ) +
  scale_y_continuous(limits = c(-3.5, 3.5)) +
  coord_cartesian(clip = "off")+
  labs(x='', y='Z-Score', fill=NULL) +
  scale_fill_manual(labels = c('High CU', 'Low CU'), values = c('#06948E', '#C1CFCA')) +
  theme_classic() + theme(axis.text.x = element_blank()) 

adi_anova<- ggplot(propensity_data_long, aes(y = value, x = name, fill = as.factor(adi_bin))) +
  geom_half_violin(
    data = subset(propensity_data_long, adi_bin == 1),
    aes(group = interaction(name, as.factor(adi_bin))),  # keep grouping explicit
    side = "l", position = position_dodge(width = 0.64),
    width = 0.8, alpha = 0.8, scale = "count", trim = FALSE
  ) +
  geom_half_violin(
    data = subset(propensity_data_long, adi_bin == 0),
    aes(group = interaction(name, as.factor(adi_bin))),
    side = "r", position = position_dodge(width = 0.4),
    width = 1, alpha = 0.8, scale = "count", trim = FALSE
  ) + geom_half_boxplot(
    data = subset(propensity_data_long, adi_bin == 1),
    aes(group = interaction(name, as.factor(adi_bin))),  # keep grouping explicit
    side = "l", position = position_dodge(width = 0.6),
    width = 0.1, alpha = 0.8, scale = "count", trim = FALSE
  ) +
  geom_half_boxplot(
    data = subset(propensity_data_long, adi_bin == 0),
    aes(group = interaction(name, as.factor(adi_bin))),
    side = "r", position = position_dodge(width = 0.6),
    width = 0.1, alpha = 0.8, scale = "count", trim = FALSE
  ) +
  scale_y_continuous(limits = c(-3.5, 3.5)) +
  coord_cartesian(clip = "off")+
  labs(x='', y='Z-Score', fill=NULL) +
  scale_fill_manual(labels = c('High ADI', 'Low ADI'), values = c('#4A8DBA','#CDE8FA')) +
  theme_classic() + theme(axis.text.x = element_blank()) 

crime_anova<- ggplot(propensity_data_long, aes(y = value, x = name, fill = as.factor(crime_bin))) +
  geom_half_violin(
    data = subset(propensity_data_long, crime_bin == 1),
    aes(group = interaction(name, as.factor(crime_bin))),  # keep grouping explicit
    side = "l", position = position_dodge(width = 0.64),
    width = 0.8, alpha = 0.8, scale = "count", trim = FALSE
  ) +
  geom_half_violin(
    data = subset(propensity_data_long, crime_bin == 0),
    aes(group = interaction(name, as.factor(crime_bin))),
    side = "r", position = position_dodge(width = 0.4),
    width = 1, alpha = 0.8, scale = "count", trim = FALSE
  ) + geom_half_boxplot(
    data = subset(propensity_data_long, crime_bin == 1),
    aes(group = interaction(name, as.factor(crime_bin))),  # keep grouping explicit
    side = "l", position = position_dodge(width = 0.6),
    width = 0.1, alpha = 0.8, scale = "count", trim = FALSE
  ) +
  geom_half_boxplot(
    data = subset(propensity_data_long, crime_bin == 0),
    aes(group = interaction(name, as.factor(crime_bin))),
    side = "r", position = position_dodge(width = 0.6),
    width = 0.1, alpha = 0.8, scale = "count", trim = FALSE
  ) +
  scale_y_continuous(limits = c(-3.5, 3.5)) +
  coord_cartesian(clip = "off")+
  labs(x='', y='Z-Score', fill=NULL) +
  scale_fill_manual(labels = c('High Crime', 'Low Crime'), values = c('#5e3c99', '#D9B4F0')) +
  theme_classic() + theme(axis.text.x = element_blank()) 

green_anova<- ggplot(propensity_data_long, aes(y = value, x = name, fill = as.factor(green_bin))) +
  geom_half_violin(
    data = subset(propensity_data_long, green_bin == 1),
    aes(group = interaction(name, as.factor(green_bin))),  # keep grouping explicit
    side = "l", position = position_dodge(width = 0.64),
    width = 0.8, alpha = 0.8, scale = "count", trim = FALSE
  ) +
  geom_half_violin(
    data = subset(propensity_data_long, green_bin == 0),
    aes(group = interaction(name, as.factor(green_bin))),
    side = "r", position = position_dodge(width = 0.4),
    width = 1, alpha = 0.8, scale = "count", trim = FALSE
  ) + geom_half_boxplot(
    data = subset(propensity_data_long, green_bin == 1),
    aes(group = interaction(name, as.factor(green_bin))),  # keep grouping explicit
    side = "l", position = position_dodge(width = 0.6),
    width = 0.1, alpha = 0.8, scale = "count", trim = FALSE
  ) +
  geom_half_boxplot(
    data = subset(propensity_data_long, green_bin == 0),
    aes(group = interaction(name, as.factor(green_bin))),
    side = "r", position = position_dodge(width = 0.6),
    width = 0.1, alpha = 0.8, scale = "count", trim = FALSE
  ) +
  scale_y_continuous(limits = c(-3.5, 3.5)) +
  coord_cartesian(clip = "off")+
  labs(x='', y='Z-Score', fill=NULL) +
  scale_fill_manual(labels = c('High Green Space', 'Low Green Space'), values = c('#5CA81E', '#C3E8A5')) +
  theme_classic() +theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))
```
```{r, warning=FALSE}
cu_anova + adi_anova + crime_anova + green_anova + 
  plot_layout(nrow = 4)
```

---
Run BCF models for T1 externalizing, estimating the ATE of CU traits 
---
```{r, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
bcf_out_con_t1 <- bcf(y         = completed_data$cbcl_scr_dsm5_conduct_t_t1,
               z                = completed_data$cu_bin,
               x_control        = as.matrix(completed_data$demo_sex_v2),
               pihat            = completed_data$p_cu,
               nburn            = 1000,
               nsim             = 1000,
               n_chains         = 4,
               random_seed      = 1,
               update_interval  = 1, 
               no_output        = TRUE)

bcf_out_opp_t1 <- bcf(y         = completed_data$cbcl_scr_dsm5_opposit_t_t1,
               z                = completed_data$cu_bin,
               x_control        = as.matrix(completed_data$demo_sex_v2),
               pihat            = completed_data$p_cu,
               nburn            = 1000,
               nsim             = 1000,
               n_chains         = 4,
               random_seed      = 1,
               update_interval  = 1, 
               no_output        = TRUE)

bcf_out_add_t1 <- bcf(y         = completed_data$cbcl_scr_dsm5_adhd_t_t1,
               z                = completed_data$cu_bin,
               x_control        = as.matrix(completed_data$demo_sex_v2),
               pihat            = completed_data$p_cu,
               nburn            = 1000,
               nsim             = 1000,
               n_chains         = 4,
               random_seed      = 1,
               update_interval  = 1, 
               no_output        = TRUE)

summary(bcf_out_con_t1)
summary(bcf_out_opp_t1)
summary(bcf_out_add_t1)
```

```{r}
save(bcf_out_con_t1, file="/Users/edenlab/OneDrive - PennO365/Double_Hit/2025/bcf_model_conduct_t1.RData")
save(bcf_out_opp_t1, file="/Users/edenlab/OneDrive - PennO365/Double_Hit/2025/bcf_model_odd_t1.RData")
save(bcf_out_add_t1, file="/Users/edenlab/OneDrive - PennO365/Double_Hit/2025/bcf_model_adhd_t1.RData")
```


```{r, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
bcf_out_con_t3 <- bcf(y         = completed_data$cbcl_scr_dsm5_conduct_t_t3,
               z                = completed_data$cu_bin,
               x_control        = as.matrix(completed_data$demo_sex_v2),
               pihat            = completed_data$p_cu,
               nburn            = 1000,
               nsim             = 1000,
               n_chains         = 4,
               random_seed      = 1,
               update_interval  = 1, 
               no_output        = TRUE)

bcf_out_opp_t3 <- bcf(y         = completed_data$cbcl_scr_dsm5_opposit_t_t3,
               z                = completed_data$cu_bin,
               x_control        = as.matrix(completed_data$demo_sex_v2),
               pihat            = completed_data$p_cu,
               nburn            = 1000,
               nsim             = 1000,
               n_chains         = 4,
               random_seed      = 1,
               update_interval  = 1, 
               no_output        = TRUE)

bcf_out_add_t3 <- bcf(y         = completed_data$cbcl_scr_dsm5_adhd_t_t3,
               z                = completed_data$cu_bin,
               x_control        = as.matrix(completed_data$demo_sex_v2),
               pihat            = completed_data$p_cu,
               nburn            = 1000,
               nsim             = 1000,
               n_chains         = 4,
               random_seed      = 1,
               update_interval  = 1, 
               no_output        = TRUE)

summary(bcf_out_con_t3)
summary(bcf_out_opp_t3)
summary(bcf_out_add_t3)
```

```{r}
save(bcf_out_con_t3, file="/Users/edenlab/OneDrive - PennO365/Double_Hit/2025/bcf_model_conduct_t3.RData")
save(bcf_out_opp_t3, file="/Users/edenlab/OneDrive - PennO365/Double_Hit/2025/bcf_model_odd_t3.RData")
save(bcf_out_add_t3, file="/Users/edenlab/OneDrive - PennO365/Double_Hit/2025/bcf_model_adhd_t3.RData")
```


---
Model CATE of CU, moderation by DICHOTOMIZED ADI, crime, and discrim on externalizing outcomes 
---

Now moderated by ADI: 
```{r, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
bcf_out_con_adi_BIN_t1 <- bcf(y   = completed_data$cbcl_scr_dsm5_conduct_t_t1,
              z                = completed_data$cu_bin,
              x_control        = as.matrix(completed_data$demo_sex_v2),
              x_moderate       = as.matrix(completed_data$adi_bin),
               pihat            = completed_data$p_cu,
               nburn            = 1000,
               nsim             = 1000,
               n_chains         = 4,
               random_seed      = 1,
               update_interval  = 1, 
               no_output        = TRUE)
bcf_out_odd_adi_BIN_t1 <- bcf(y   = completed_data$cbcl_scr_dsm5_opposit_t_t1,
               z                = completed_data$cu_bin,
               x_control        = as.matrix(completed_data$demo_sex_v2),
               x_moderate       = as.matrix(completed_data$adi_bin),
               pihat            = completed_data$p_cu,
               nburn            = 1000,
               nsim             = 1000,
               n_chains         = 4,
               random_seed      = 1,
               update_interval  = 1, 
               no_output        = TRUE)
bcf_out_add_adi_BIN_t1 <- bcf(y   = completed_data$cbcl_scr_dsm5_adhd_t_t1,
               z                = completed_data$cu_bin,
               x_control        = as.matrix(completed_data$demo_sex_v2),
               x_moderate       = as.matrix(completed_data$adi_bin),
               pihat            = completed_data$p_cu,
               nburn            = 1000,
               nsim             = 1000,
               n_chains         = 4,
               random_seed      = 1,
               update_interval  = 1, 
               no_output        = TRUE)
```

```{r}
save(bcf_out_con_adi_BIN_t1, file="/Users/edenlab/OneDrive - PennO365/Double_Hit/2025/bcf_model_conduct_adi_BIN_t1.RData")
save(bcf_out_odd_adi_BIN_t1, file="/Users/edenlab/OneDrive - PennO365/Double_Hit/2025/bcf_model_odd_adi_BIN_t1.RData")
save(bcf_out_add_adi_BIN_t1, file="/Users/edenlab/OneDrive - PennO365/Double_Hit/2025/bcf_model_adhd_adi_BIN_t1.RData")
```

And crime: 
```{r, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
bcf_out_con_crime_BIN_t1 <- bcf(y   = completed_data$cbcl_scr_dsm5_conduct_t_t1,
              z                = completed_data$cu_bin,
               x_control        = as.matrix(completed_data$demo_sex_v2),
               x_moderate       = as.matrix(completed_data$crime_bin),
               pihat            = completed_data$p_cu,
               nburn            = 1000,
               nsim             = 1000,
               n_chains         = 4,
               random_seed      = 1,
               update_interval  = 1, 
               no_output        = TRUE)

bcf_out_odd_crime_BIN_t1 <- bcf(y   = completed_data$cbcl_scr_dsm5_opposit_t_t1,
               z                = completed_data$cu_bin,
               x_control        = as.matrix(completed_data$demo_sex_v2),
               x_moderate       = as.matrix(completed_data$crime_bin),
               pihat            = completed_data$p_cu,
               nburn            = 1000,
               nsim             = 1000,
               n_chains         = 4,
               random_seed      = 1,
               update_interval  = 1, 
               no_output        = TRUE)

bcf_out_add_crime_BIN_t1 <- bcf(y   = completed_data$cbcl_scr_dsm5_adhd_t_t1,
               z                = completed_data$cu_bin,
               x_control        = as.matrix(completed_data$demo_sex_v2),
               x_moderate       = as.matrix(completed_data$crime_bin),
               pihat            = completed_data$p_cu,
               nburn            = 1000,
               nsim             = 1000,
               n_chains         = 4,
               random_seed      = 1,
               update_interval  = 1, 
               no_output        = TRUE)

```

```{r}
save(bcf_out_con_crime_BIN_t1, file="/Users/edenlab/OneDrive - PennO365/Double_Hit/2025/bcf_model_conduct_crime_BIN_t1.RData")
save(bcf_out_odd_crime_BIN_t1, file="/Users/edenlab/OneDrive - PennO365/Double_Hit/2025/bcf_model_odd_crime_BIN_t1.RData")
save(bcf_out_add_crime_BIN_t1, file="/Users/edenlab/OneDrive - PennO365/Double_Hit/2025/bcf_model_adhd_crime_BIN_t1.RData")
```

And green space
```{r, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
bcf_out_con_green_BIN_t1 <- bcf(y   = completed_data$cbcl_scr_dsm5_conduct_t_t1,
               z                = completed_data$cu_bin,
               x_control        = as.matrix(completed_data$demo_sex_v2),
               x_moderate       = as.matrix(completed_data$green_bin),
               pihat            = completed_data$p_cu,
               nburn            = 1000,
               nsim             = 1000 ,
               n_chains         = 4,
               random_seed      = 1,
               update_interval  = 1, 
               no_output        = TRUE)

bcf_out_odd_green_BIN_t1 <- bcf(y   = completed_data$cbcl_scr_dsm5_opposit_t_t1,
              z                = completed_data$cu_bin,
               x_control        = as.matrix(completed_data$demo_sex_v2),
               x_moderate       = as.matrix(completed_data$green_bin),
               pihat            = completed_data$p_cu,
               nburn            = 1000,
               nsim             = 1000 ,
               n_chains         = 4,
               random_seed      = 1,
               update_interval  = 1, 
               no_output        = TRUE)

bcf_out_add_green_BIN_t1 <- bcf(y   = completed_data$cbcl_scr_dsm5_adhd_t_t1,
              z                = completed_data$cu_bin,
               x_control        = as.matrix(completed_data$demo_sex_v2),
               x_moderate       = as.matrix(completed_data$green_bin),
               pihat            = completed_data$p_cu,
               nburn            = 1000,
               nsim             = 1000,
               n_chains         = 4,
               random_seed      = 1,
               update_interval  = 1, 
               no_output        = TRUE)   

```

```{r}
save(bcf_out_con_green_BIN_t1, file="/Users/edenlab/OneDrive - PennO365/Double_Hit/2025/bcf_model_conduct_green_BIN_t1.RData")
save(bcf_out_odd_green_BIN_t1, file="/Users/edenlab/OneDrive - PennO365/Double_Hit/2025/bcf_model_odd_green_BIN_t1.RData")
save(bcf_out_add_green_BIN_t1, file="/Users/edenlab/OneDrive - PennO365/Double_Hit/2025/bcf_model_adhd_green_BIN_t1.RData")
```

Now moderated by ADI: 
```{r, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
bcf_out_con_adi_BIN_t3 <- bcf(y   = completed_data$cbcl_scr_dsm5_conduct_t_t3,
               z                = completed_data$cu_bin,
               x_control        = as.matrix(completed_data$demo_sex_v2),
               x_moderate       = as.matrix(completed_data$adi_bin),
               pihat            = completed_data$p_cu,
               nburn            = 1000,
               nsim             = 1000,
               n_chains         = 4,
               random_seed      = 1,
               update_interval  = 1, 
               no_output        = TRUE)
bcf_out_odd_adi_BIN_t3 <- bcf(y   = completed_data$cbcl_scr_dsm5_opposit_t_t3,
               z                = completed_data$cu_bin,
               x_control        = as.matrix(completed_data$demo_sex_v2),
               x_moderate       = as.matrix(completed_data$adi_bin),
               pihat            = completed_data$p_cu,
               nburn            = 1000,
               nsim             = 1000,
               n_chains         = 4,
               random_seed      = 1,
               update_interval  = 1, 
               no_output        = TRUE)

bcf_out_add_adi_BIN_t3 <- bcf(y   = completed_data$cbcl_scr_dsm5_adhd_t_t3,
               z                = completed_data$cu_bin,
               x_control        = as.matrix(completed_data$demo_sex_v2),
               x_moderate       = as.matrix(completed_data$adi_bin),
               pihat            = completed_data$p_cu,
               nburn            = 1000,
               nsim             = 1000,
               n_chains         = 4,
               random_seed      = 1,
               update_interval  = 1, 
               no_output        = TRUE)
```

```{r}
save(bcf_out_con_adi_BIN_t3, file="/Users/edenlab/OneDrive - PennO365/Double_Hit/2025/bcf_model_conduct_adi_BIN_t3.RData")
save(bcf_out_odd_adi_BIN_t3, file="/Users/edenlab/OneDrive - PennO365/Double_Hit/2025/bcf_model_odd_adi_BIN_t3.RData")
save(bcf_out_add_adi_BIN_t3, file="/Users/edenlab/OneDrive - PennO365/Double_Hit/2025/bcf_model_adhd_adi_BIN_t3.RData")
```


And crime: 
```{r}
bcf_out_con_crime_BIN_t3 <- bcf(y   = completed_data$cbcl_scr_dsm5_conduct_t_t3,
               z                = completed_data$cu_bin,
               x_control        = as.matrix(completed_data$demo_sex_v2),
               x_moderate       = as.matrix(completed_data$crime_bin),
               pihat            = completed_data$p_cu,
               nburn            = 1000,
               nsim             = 1000,
               n_chains         = 4,
               random_seed      = 1,
               update_interval  = 1, 
               no_output        = TRUE)

bcf_out_odd_crime_BIN_t3 <- bcf(y   = completed_data$cbcl_scr_dsm5_opposit_t_t3,
               z                = completed_data$cu_bin,
               x_control        = as.matrix(completed_data$demo_sex_v2),
               x_moderate       = as.matrix(completed_data$crime_bin),
               pihat            = completed_data$p_cu,
               nburn            = 1000,
               nsim             = 1000,
               n_chains         = 4,
               random_seed      = 1,
               update_interval  = 1, 
               no_output        = TRUE)

bcf_out_add_crime_BIN_t3 <- bcf(y   = completed_data$cbcl_scr_dsm5_adhd_t_t3,
               z                = completed_data$cu_bin,
               x_control        = as.matrix(completed_data$demo_sex_v2),
               x_moderate       = as.matrix(completed_data$crime_bin),
               pihat            = completed_data$p_cu,
               nburn            = 1000,
               nsim             = 1000,
               n_chains         = 4,
               random_seed      = 1,
               update_interval  = 1, 
               no_output        = TRUE)
```

```{r}
save(bcf_out_con_crime_BIN_t3, file="/Users/edenlab/OneDrive - PennO365/Double_Hit/2025/bcf_model_conduct_crime_BIN_t3.RData")
save(bcf_out_odd_crime_BIN_t3, file="/Users/edenlab/OneDrive - PennO365/Double_Hit/2025/bcf_model_odd_crime_BIN_t3.RData")
save(bcf_out_add_crime_BIN_t3, file="/Users/edenlab/OneDrive - PennO365/Double_Hit/2025/bcf_model_adhd_crime_BIN_t3.RData")
```


```{r, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
bcf_out_con_green_BIN_t3 <- bcf(y   = completed_data$cbcl_scr_dsm5_conduct_t_t3,
               z                = completed_data$cu_bin,
               x_control        = as.matrix(completed_data$demo_sex_v2),
               x_moderate       = as.matrix(completed_data$green_bin),               
               pihat            = completed_data$p_cu,
               nburn            = 1000,
               nsim             = 1000 ,
               n_chains         = 4,
               random_seed      = 1,
               update_interval  = 1, 
               no_output        = TRUE)

bcf_out_odd_green_BIN_t3 <- bcf(y   = completed_data$cbcl_scr_dsm5_opposit_t_t3,
               z                = completed_data$cu_bin,
               x_control        = as.matrix(completed_data$demo_sex_v2),
               x_moderate       = as.matrix(completed_data$green_bin),
               pihat            = completed_data$p_cu,
               nburn            = 1000,
               nsim             = 1000 ,
               n_chains         = 4,
               random_seed      = 1,
               update_interval  = 1, 
               no_output        = TRUE)

bcf_out_add_green_BIN_t3 <- bcf(y   = completed_data$cbcl_scr_dsm5_adhd_t_t3,
               z                = completed_data$cu_bin,
               x_control        = as.matrix(completed_data$demo_sex_v2),
               x_moderate       = as.matrix(completed_data$green_bin),
               pihat            = completed_data$p_cu,
               nburn            = 1000,
               nsim             = 1000,
               n_chains         = 4,
               random_seed      = 1,
               update_interval  = 1, 
               no_output        = TRUE)   
```

```{r}
save(bcf_out_con_green_BIN_t3, file="/Users/edenlab/OneDrive - PennO365/Double_Hit/2025/bcf_model_conduct_green_BIN_t3.RData")
save(bcf_out_odd_green_BIN_t3, file="/Users/edenlab/OneDrive - PennO365/Double_Hit/2025/bcf_model_odd_green_BIN_t3.RData")
save(bcf_out_add_green_BIN_t3, file="/Users/edenlab/OneDrive - PennO365/Double_Hit/2025/bcf_model_adhd_green_BIN_t3.RData")
```

