---
title: "R Notebook"
output: html_notebook
---

This notebook makes plots for different geocoded outcomes. 

First, load pacakges:
```{r}
library(tidycensus)
library(segregation)
library(sf)
library(dplyr)
library(tigris); options(tigris_use_cache = TRUE, tigris_class = "sf")
```

Next, activate census API key to get data: 
```{r}
#census_api_key("a87750e90a085eca30a55092960ed348457fea91", install = TRUE)
```
---
ADI
---
Load ADI from download:
```{r}
adi<- read.csv('~/Downloads/adi-download-2/US_2023_ADI_Census_Block_Group_v4_0_1.csv')%>%
  mutate(FIPS = as.character(FIPS))
```

Convert to GEOID:
```{r}
adi_bg <- adi %>%                    
  mutate(
    FIPS  = as.character(FIPS),          
    GEOID = str_pad(FIPS, 12, pad = "0"))
```

Get block groups for PA, CA and WA and join with adi
```{r}
block_groups_pa <- block_groups(state = "PA", year = 2023, cb = TRUE)  
block_groups_ca <- block_groups(state = "CA", year = 2023, cb = TRUE)  
block_groups_mo <- block_groups(state = "MO", year = 2023, cb = TRUE)
block_groups_wa <- block_groups(state = "WA", year = 2023, cb = TRUE)
block_groups_or <- block_groups(state = "OR", year = 2023, cb = TRUE)
block_groups_il <- block_groups(state = "IL", year = 2023, cb = TRUE)

block_groups<- rbind(block_groups_pa, block_groups_mo, block_groups_ca, block_groups_or, block_groups_wa, block_groups_il)

bg_adi <- dplyr::left_join(block_groups, adi_bg, by = "GEOID")    %>%
   mutate(ADI_NATRANK = as.numeric(ADI_NATRANK))# keeps geometry
```

Pin to just cities 
```{r}
pittsburgh <- places(state = "PA", year = 2023, cb = TRUE) %>% filter(NAME == "Pittsburgh")
losangeles <- places(state = "CA", year = 2023, cb = TRUE) %>% filter(NAME == "Los Angeles")
stlouis <- places(state = "MO", year = 2023, cb = TRUE) %>% filter(NAME == "St. Louis")
portland <- places(state = "OR", year = 2023, cb = TRUE) %>% filter(NAME == "Portland")

cities_sf<- rbind(pittsburgh, losangeles, stlouis, portland)

bg_adi_city <- st_filter(bg_adi, cities_sf)%>%
  mutate(ADI_NATRANK = as.numeric(ADI_NATRANK))
bg_adi_city <- st_join(bg_adi_city, cities_sf %>% select(NAME), join = st_intersects)

# make sure it's a factor so facet_wrap shows names, not 1..7
bg_adi_city <- bg_adi_city %>%
  mutate(NAME = as.factor(NAME.y))
```

Plot ADI: 
```{r}
custom_colors_adi <- colorRampPalette(c("#F1F1F1","#4A8DBA"))

or_adi<- bg_adi %>% filter(STATEFP%in% c('41', '53'))%>%
  ggplot() +
  geom_sf(aes(fill = ADI_NATRANK)) +
  scale_fill_gradientn(colors = custom_colors_adi(5)) +
  coord_sf(
  xlim = c(-122.9, -122.4),
  ylim = c( 45.70, 45.40))+
  theme_void() +
  labs(fill = "ADI")
or_adi

pa_adi<- bg_adi %>% filter(STATEFP%in% c('42'))%>%
  ggplot() +
  geom_sf(aes(fill = ADI_NATRANK)) +
  scale_fill_gradientn(colors = custom_colors_adi(5)) +
  coord_sf(
  xlim = c(-80.15, -79.85),
  ylim = c( 40.55, 40.35))+
  theme_void() +
  labs(fill = "ADI")
pa_adi

mo_adi<- bg_adi %>% filter(STATEFP%in% c('29', '17'))%>%
  ggplot() +
  geom_sf(aes(fill = ADI_NATRANK)) +
  scale_fill_gradientn(colors = custom_colors_adi(5)) +
  coord_sf(
  xlim = c(-90.35, -90),
  ylim = c( 38.55, 38.825))+
  theme_void() +
  labs(fill = "ADI")
mo_adi
```

```{r}
adi<-box_read('1277087025313', fread=TRUE)
adi<-adi%>%
  filter(eventname=="baseline_year_1_arm_1")%>%
  mutate(adi_bin = case_when(reshist_addr1_adi_wsum <= 87.862045 ~ 0, #low deprivation
                             reshist_addr1_adi_wsum >= 108.394920 ~ 1))%>% #high deprivation
  select(src_subject_id, reshist_addr1_adi_wsum, adi_bin)


density_adi<- ggplot(adi, aes(y = reshist_addr1_adi_wsum)) +
  stat_density(
    aes(x = -after_stat(density)),
    geom = "area",
    fill = "#4A8DBA",color ='#4A8DBA',
    alpha = 0.5
  ) + scale_y_continuous(limits = c(0, 130)) +theme_void()

density_adi
```

---
CRIME
---
Now read in crime and filter for PA, MO, and OR
```{r}
crime<- read.table('~/Downloads/ICPSR_33523-2/DS0004/33523-0004-Data.tsv', sep="\t", header=T)%>%
  filter(FIPS_ST %in% c(6, 29, 41, 42, 17, 53, 54, 39, 24))%>%
  rowwise()%>%
  mutate(total_crime = VIOL + PROPERTY + MURDER +RAPE +ROBBERY+ AGASSLT+ BURGLRY+LARCENY+MVTHEFT)%>%
  mutate(FIPS_ST = str_pad(FIPS_ST, 2, pad = "0"))%>%
  mutate(FIPS_CTY = str_pad(FIPS_CTY, 3, pad = "0"))%>%
  mutate(GEOID = paste0(FIPS_ST, FIPS_CTY))
```

Get counties for PA, CA and WA and join with adi
```{r}
counties_pa <- counties(state = c("PA", "WV", "OH", "MD"), year = 2023, cb = TRUE)  
counties_mo <- counties(state = c("MO", "IL"), year = 2023, cb = TRUE)
counties_or <- counties(state = c("OR", "WA"), year = 2023, cb = TRUE)

counties<- rbind(counties_pa, counties_mo, counties_or)%>%
  mutate(FIPS_CTY = GEOID)

bg_crime <- left_join(counties, crime, by = "GEOID")
```

```{r}
custom_colors_crime <- colorRampPalette(c("#F1F1F1","#5e3c99"))

pa_crime<- bg_crime %>% filter(STATE_NAME%in% c('Pennsylvania', 'West Virginia', 'Ohio', 'Maryland'))%>%
  ggplot() +
  geom_sf(aes(fill = total_crime)) +
  scale_fill_gradientn(colors = custom_colors_crime(5), limits=c(0, 102678)) +
  coord_sf(xlim = c(-81.1779, -78.8139), ylim = c(39.5406, 41.3406))+
  theme_void() +
  labs(fill = "Total Crime")
pa_crime


or_crime<- bg_crime %>% filter(STATE_NAME %in% c('Oregon', 'Washington'))%>%
  ggplot() +
  geom_sf(aes(fill = total_crime)) +
  scale_fill_gradientn(colors = custom_colors_crime(5), limits=c(0, 102678)) +
  coord_sf(
  xlim = c(-122.6765 - 1.282,  -122.6765 + 1.282),
  ylim = c( 45.5231 - 0.900,    45.5231 + 0.900))+
  theme_void() +
  labs(fill = "Total Crime")
or_crime

mo_crime<- bg_crime %>% filter(STATE_NAME%in% c('Missouri', 'Illinois'))%>%
  ggplot() +
  geom_sf(aes(fill = total_crime)) +
  scale_fill_gradientn(colors = custom_colors_crime(5),  limits=c(0, 102678)) +
  coord_sf(
  xlim = c(-91.3624, -89.0364), ylim = c(37.7270, 39.5270))+
  theme_void() +
  labs(fill = "Total Crime")
mo_crime
```

```{r}
crime<-box_read('1277095261533', fread=TRUE)
crime<- crime%>%
  filter(eventname=="baseline_year_1_arm_1")%>%
  select(src_subject_id, reshist_addr1_grndtot)%>%
  mutate(crime_log = (reshist_addr1_grndtot +1)^1/3)%>%
  mutate(crime_bins = cut(reshist_addr1_grndtot, breaks = 6))%>%
  mutate(crime_bin = case_when(reshist_addr1_grndtot <= 7832.00 ~ 0, 
                               reshist_addr1_grndtot >= 53399.67 ~ 1))


density_crime<- ggplot(crime, aes(y = reshist_addr1_grndtot)) +
  stat_density(
    aes(x = -after_stat(density)),
    geom = "area",
    fill = "#5e3c99",color ='#5e3c99',
    alpha = 0.5
  ) +scale_y_continuous(0, 348050) +theme_void()

density_crime
```

---
Green space
---
get park data (prop_park_area_tract)
```{r}
green<- read.table('~/Downloads/ICPSR_38586/DS0003/38586-0003-Data.tsv', sep="\t", header=T)%>%
  mutate(GEOID = as.character(TRACT_FIPS20))
```

Get block groups for PA, CA and WA and join with adi
```{r}
tract_groups_pa <- tracts(state = "PA", year = 2023, cb = TRUE)  
tract_groups_ca <- tracts(state = "CA", year = 2023, cb = TRUE)  
tract_groups_mo <- tracts(state = "MO", year = 2023, cb = TRUE)
tract_groups_wa <- tracts(state = "WA", year = 2023, cb = TRUE)
tract_groups_il <- tracts(state = "IL", year = 2023, cb = TRUE)
tract_groups_or <- tracts(state = "OR", year = 2023, cb = TRUE)

tract_groups<- rbind(tract_groups_pa, tract_groups_mo, tract_groups_ca, tract_groups_or, tract_groups_wa, tract_groups_il)

bg_green <- dplyr::left_join(tract_groups, green, by = "GEOID")       # keeps geometry
```

Pin to just cities 
```{r}
pittsburgh <- places(state = "PA", year = 2023, cb = TRUE) %>% filter(NAME == "Pittsburgh")
losangeles <- places(state = "CA", year = 2023, cb = TRUE) %>% filter(NAME == "Los Angeles")
stlouis <- places(state = "MO", year = 2023, cb = TRUE) %>% filter(NAME == "St. Louis")
portland <- places(state = "OR", year = 2023, cb = TRUE) %>% filter(NAME == "Portland")

cities_sf<- rbind(pittsburgh, losangeles, stlouis, portland)

bg_green_city <- st_filter(bg_green, cities_sf)
bg_green_city <- st_join(bg_green_city, cities_sf %>% select(NAME), join = st_intersects)

# make sure it's a factor so facet_wrap shows names, not 1..7
bg_green_city <- bg_green_city %>%
  mutate(NAME = as.factor(NAME.y))
```

```{r}
custom_colors_green <- colorRampPalette(c("#F1F1F1","#5CA81E"))

or_green<- bg_green %>% filter(STATE_NAME%in% c('Oregon', 'Washington'))%>%
  ggplot() +
  geom_sf(aes(fill = PROP_PARK_AREA_TRACT)) +
  scale_fill_gradientn(colors = custom_colors_green(5)) +
  coord_sf(
  xlim = c(-122.9, -122.4),
  ylim = c( 45.70, 45.40))+
  theme_void() +
  labs(fill = "Proportion Green Space")
or_green

pa_green<- bg_green %>% filter(STATE_NAME%in% c('Pennsylvania'))%>%
  ggplot() +
  geom_sf(aes(fill = PROP_PARK_AREA_TRACT)) +
  scale_fill_gradientn(colors = custom_colors_green(5)) +
  coord_sf(
  xlim = c(-80.15, -79.85),
  ylim = c( 40.55, 40.35))+
  theme_void() +
  labs(fill = "Proportion Green Space")
pa_green

mo_green<- bg_green %>% filter(STATE_NAME%in% c('Missouri', 'Illinois'))%>%
  ggplot() +
  geom_sf(aes(fill = PROP_PARK_AREA_TRACT)) +
  scale_fill_gradientn(colors = custom_colors_green(5)) +
  coord_sf(
  xlim = c(-90.35, -90),
  ylim = c( 38.55, 38.825))+
  labs(fill = "Proportion Green Space") +theme_void()
mo_green
```

```{r}
#read in greenspace
green<-box_read('1277088493816', fread=TRUE)
green<-green%>%
  filter(eventname=="baseline_year_1_arm_1")%>%
  mutate(green_bin = case_when(reshist_addr1_coi_he_green <= 14 ~ 0, #low green
                             reshist_addr1_coi_he_green >= 48.025 ~ 1))%>% #high green
  select(src_subject_id, reshist_addr1_coi_he_green, green_bin)

density_green<- ggplot(green, aes(y = reshist_addr1_coi_he_green)) +
  stat_density(
    aes(x = -after_stat(density)),
    geom = "area",
    fill = "#5CA81E",color ='#5CA81E',
    alpha = 0.5
  )  +theme_void()

density_green
```

arrange: 
```{r}
(density_adi + or_adi + pa_adi + mo_adi +
 density_green + or_green + pa_green + mo_green +
 density_crime + or_crime + pa_crime + mo_crime) +
  plot_layout(ncol = 4, guides = "collect") &
  theme(
    legend.position = "right",
    plot.margin = margin(5, 5, 5, 5)
  )
```
```{r}
ggsave(file="density_adi.svg", plot=density_adi, width=8, height=8)
ggsave(file="density_green.svg", plot=density_green, width=8, height=8)
ggsave(file="density_crime.svg", plot=density_crime, width=8, height=8)

ggsave(file="or_adi.svg", plot=or_adi, width=8.5, height=8)
ggsave(file="pa_adi.svg", plot=pa_adi, width=8.5, height=8)
ggsave(file="mo_adi.svg", plot=mo_adi, width=8.5, height=8)

ggsave(file="or_green.svg", plot=or_green, width=8.5, height=8)
ggsave(file="pa_green.svg", plot=pa_green, width=8.5, height=8)
ggsave(file="mo_green.svg", plot=mo_green, width=8.5, height=8)

ggsave(file="or_crime.svg", plot=or_crime, width=8.5, height=8)
ggsave(file="pa_crime.svg", plot=pa_crime, width=8.5, height=8)
ggsave(file="mo_crime.svg", plot=mo_crime, width=8.5, height=8)
```

```
